### 2025-01-20 README.Rmd
Small changes to text

This repository contains the bremla package (**B**ayesian **Re**gression **M**odeling of **L**ayer-counted **a**rchives) for uncertainty quantification and synchronization for layer-counted proxy archives, including the data and code to reproduce the results for

@@

Myrvoll-Nilsen, E., Riechers, K. & Boers, N. (202x). Tie-point paper (title TBD)

>>>>

This repository contains the bremla package (**B**ayesian **Re**gression **M**odeling of **L**ayer-counted **a**rchives) for uncertainty quantification and synchronization for layer-counted proxy archives. This repository also includes, in the 'inst/' folder, the data and code to reproduce the results for

@@

Myrvoll-Nilsen, E., Riechers, K. & Boers, N. (2025). Synchronization of layer-counted paleoclimatic proxy archives using a Bayesian regression modeling framework. Bayesian Analysis. In review.

### 2025-01-20 inst/reproduce_results_BA/results.Rmd
Small changes to text

@@

ggdreal0 = data.frame(depth=object0$data$depth, age=object0$data$age, agemean= object0$simulation$summary$mean, agelower = object0$simulation$summary$lower, ageupper=object0$simulation$summary$upper, sagemean=object0$simulation$summary_sync$mean, 
                 sagelower=object0$simulation$summary_sync$lower, sageupper=object0$simulation$summary_sync$upper,
                 agediffmean=object0$simulation$summary$mean-object0$data$age,
                 agedifflower=object0$simulation$summary$lower-object0$data$age, 
                 agediffupper=object0$simulation$summary$upper-object0$data$age,
                 sagediffmean=object0$simulation$summary_sync$mean-object0$data$age,
                 sagedifflower=object0$simulation$summary_sync$lower-object0$data$age,
                 sagediffupper=object0$simulation$summary_sync$upper-object0$data$age)

@@

```{r}
ggdreal = data.frame(depth=object$data$depth, age=object$data$age, agemean= object$simulation$summary$mean, agelower = object$simulation$summary$lower, ageupper=object$simulation$summary$upper, sagemean=object$simulation$summary_sync$mean, 
                 sagelower=object$simulation$summary_sync$lower, sageupper=object$simulation$summary_sync$upper,
                 agediffmean=object$simulation$summary$mean-object$data$age,
                 agedifflower=object$simulation$summary$lower-object$data$age, 
                 agediffupper=object$simulation$summary$upper-object$data$age,
                 sagediffmean=object$simulation$summary_sync$mean-object$data$age,
                 sagedifflower=object$simulation$summary_sync$lower-object$data$age,
                 sagediffupper=object$simulation$summary_sync$upper-object$data$age)

>>>>

#### Plot results
This code generates the plots included in the paper. The important results can be illustrated simply by using 'plot(object0)', but this code also includes the shaded area representing the unsynchronized chronology ensemble.

@@

#plot(object0)
ggdreal0 = data.frame(depth=object0$data$depth, age=object0$data$age, agemean= object0$simulation$summary$mean, agelower = object0$simulation$summary$lower, ageupper=object0$simulation$summary$upper, sagemean=object0$simulation$summary_sync$mean, 
                 sagelower=object0$simulation$summary_sync$lower, sageupper=object0$simulation$summary_sync$upper,
                 agediffmean=object0$simulation$summary$mean-object0$data$age,
                 agedifflower=object0$simulation$summary$lower-object0$data$age, 
                 agediffupper=object0$simulation$summary$upper-object0$data$age,
                 sagediffmean=object0$simulation$summary_sync$mean-object0$data$age,
                 sagedifflower=object0$simulation$summary_sync$lower-object0$data$age,
                 sagediffupper=object0$simulation$summary_sync$upper-object0$data$age)

@@

#plot(object)
ggdreal = data.frame(depth=object$data$depth, age=object$data$age, agemean= object$simulation$summary$mean, agelower = object$simulation$summary$lower, ageupper=object$simulation$summary$upper, sagemean=object$simulation$summary_sync$mean, 
                 sagelower=object$simulation$summary_sync$lower, sageupper=object$simulation$summary_sync$upper,
                 agediffmean=object$simulation$summary$mean-object$data$age,
                 agedifflower=object$simulation$summary$lower-object$data$age, 
                 agediffupper=object$simulation$summary$upper-object$data$age,
                 sagediffmean=object$simulation$summary_sync$mean-object$data$age,
                 sagedifflower=object$simulation$summary_sync$lower-object$data$age,
                 sagediffupper=object$simulation$summary_sync$upper-object$data$age)
